---
title: "project1"
author: "cherry"
date: "10/9/2019"
output: html_document
---

```{r basicfcn, include=F}
# can add quietly=T option to the require() function
loadPkg = function(x) { if (!require(x,character.only=T, quietly =T)) { install.packages(x,dep=T,repos="http://cran.us.r-project.org"); if(!require(x,character.only=T)) stop("Package not found") } }
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load the library
library(dplyr)
library(ggplot2)

# Load the dataset
crime <- read.csv("../DataSet/Crime_Incidents_in_2018.csv")
```

## Chapter 4: Time

### 4.2 Report Time

From the dataset, we also found that there exists different time gap between the date of report and crime. Are the time gap in different crime types is just random or there are some correlations among them. In this part, we will explore more on this.

#### 4.2.1 SMART Question

Does the time difference between report date and crime date have a correlation with the type of crimes?

#### 4.2.2 Basic Analysis of time difference

First, for the raw dataset only have columns report date and crime date, we need to acquire the time difference and created a new column named ‘ time difference ’that calculated by using column’ report_date’ subtracting column ‘ start_date’

```{r, echo = F}
crimeTime <- subset(crime, select = c(REPORT_DAT, START_DATE))
# levels(crimeTime$REPORT_DAT)
# crimeTime

# strptime(crime$REPORT_DAT[1],format = "%Y-%m-%d %H:%M:%S")
crimeTime$REPORT_DAT <- as.POSIXct(gsub(".000Z", "", gsub("T", " ", as.character(crimeTime$REPORT_DAT))))
#crimeTime$REPORT_DAT <- gsub("T"," ", crimeTime$REPORT_DAT)
#crimeTime$REPORT_DAT <- gsub(".000Z","", crimeTime$REPORT_DAT)
#crimeTime$REPORT_DAT <- as.POSIXct(crimeTime$REPORT_DAT)

crimeTime$START_DATE <- as.POSIXct(gsub(".000Z", "", gsub("T", " ", as.character(crimeTime$START_DATE))))

crimeTime <- crimeTime %>% 
  mutate(Time_Difference = difftime(REPORT_DAT, START_DATE))

crimeTime$Time_Difference <- as.numeric(crimeTime$Time_Difference)

head(crimeTime)
```

Then, Grouping time difference by crime types  (offense), we can observe the differences in time differences as well as some outliers in each group.

```{r, echo = F}
crimeOffense <- subset(crime, select = 'OFFENSE')
crimeTimeAndOffense<- cbind(crimeTime, crimeOffense)

crimeTimeAndOffense <- subset(crimeTimeAndOffense, (Time_Difference <= 10000 & Time_Difference >= 0))
head(crimeTimeAndOffense)
```

—-box plot (time)

```{r, echo = F}
boxplot(crimeTimeAndOffense$Time_Difference, col = "orange", main = "boxplot of difftime")
```

—-statistics in different crime types

```{r, echo = F}

p <- ggplot(crimeTimeAndOffense, aes(x=OFFENSE, y=Time_Difference, color = OFFENSE)) + 
  ggtitle("boxplot of Time with Offense") + 
  geom_boxplot()

p + scale_x_discrete(breaks = levels(crimeTimeAndOffense$OFFENSE), labels = c('ARS','AW/DW','BUR','HOM','MOT','ROB','SA','TF/A','T/O'))
```

#### 4.2.3 Are time difference the same across all crime types?

H0: 
H1: They are different.
We use ANOVA to test the hypothesis, and calculate the p-value.

```{r, echo =F }
anovaCrime <- aov(Time_Difference~OFFENSE, data = crimeTimeAndOffense)
anovaCrime
summary(anovaCrime)
```

#### 4.2.4 Further more interesting guess (according to the results)
