---
title: "part2"
author: "Zichu"
date: "10/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
crime <- read.csv("../Dataset/Crime_Incidents_in_2018.csv")
crime <- data.frame(crime)
library(ggplot2)
```

```{r}
library(lubridate)
getSeason <- function(input.date){
  numeric.date <- 100*month(input.date)+day(input.date)
  ## input Seasons upper limits in the form MMDD in the "break =" option:
  cuts <- base::cut(numeric.date, breaks = c(0,319,0620,0921,1220,1231)) 
  # rename the resulting groups (could've been done within cut(...levels=) if "Winter" wasn't double
  levels(cuts) <- c("Winter","Spring","Summer","Fall","Winter")
  return(cuts)
}
```

## Chapter 2: Crime Time

The dataset include specific crime time including date and time in 2018 year, therefore we can derive our insights into it. Firstly, we explore the crime occurrence distribution in different crime time. Secondly, we take a look at the relationship between crime offense and crime time.

### 2.1 SMART Question

Does crime occurrence frequency and crime offense differ by crime time including seasons in one year and time in one day?

### 2.2 Basic Data Processing of crime time

Firstly, we add two new columns into the dataset according to the "start_date" and group them into "crimemonth" and "crimeseason"(We select Months in Dec, Jan and Feb as winter). Later we will use these two variables with frequency of crime occurrence to analyze more.

```{r}
library(lubridate)
crimedate <- crime$START_DATE
crime$crimemonth<- month(as.POSIXlt(crimedate, format="%Y-%m-%dT%H:%M:%S.000Z"))
crime$crimeseason<- getSeason(as.POSIXlt(crimedate, format="%Y-%m-%dT%H:%M:%S.000Z"))
crime$crimemonth<- as.factor((crime$crimemonth))
summary(crime$crimemonth)
summary(crime$crimeseason)
```

### 2.3 crime occurrence frequency during different time

```{r}
seasonsummary=data.frame(A=c(7136,7892,9709,9046),B=c("Winter","Spring","Summer","Fall"))
ggplot(seasonsummary, aes(x = "", y = A, fill = B)) + 
  geom_bar(stat = "identity") + 
  coord_polar(theta = "y") + 
  xlab("Count") +
  scale_fill_discrete(name = "Season") 
```

```{r}
#plot(crime$crimemonth)
season1=factor(crime$crimeseason,levels=c("Spring","Summer","Fall","Winter"))
colorbar1=c("green","red","yellow","blue")

ggplot() + 
  geom_bar(aes(x = crime$crimemonth, fill = crime$crimemonth)) +
  xlab("Month") +
  scale_fill_discrete(name = "Month")
```

First,the pie chart which shows the crime frequency in different seasons. We can find that the frequency in Autumn and Summer accounts most. Next, we take a look at the first bar plot and it shows the crime occurence in different months in 2018. The tendency of frequency distribution shows central high and two edges low. It appears that during the summer, there are more likely to occur crime. The most crime incidence month is August and the frequency is 3334.The fewest is in February belonging to winter and the frequency is 2321.

```{r}
ggplot() + 
  geom_bar(aes(x = crime$SHIFT, fill = crime$SHIFT)) + 
  xlab("SHIFT") +
  scale_fill_discrete(name = "Shift") 
summary(crime$SHIFT)
```
This bar plot shows the crime frequency in different shift in one day. We divide one day into three parts, which are Day, Evening and Midnight. From the results, we can see that most crime occur at evening and the frequency is 14394. The fewes crime occur in the day and the frequency is 12150.

### 2.4 crime offense during different time
```{r}
spring <- subset(crime,crimeseason=="Spring")
summer <- subset(crime,crimeseason=="Summer")
autumn <- subset(crime,crimeseason=="Autumn")
winter <- subset(crime,crimeseason=="Winter")
spof <- summary(spring$OFFENSE)
smof <- summary(summer$OFFENSE)
atof <- summary(autumn$OFFENSE)
wtaf <- summary(winter$OFFENSE)
```

```{r}
summary(crime$SHIFT)
#plot(crime$SHIFT, col = c("red", "yellow", "blue"))
ggplot() + 
  geom_bar(aes(x = crime$OFFENSE, fill = crime$SHIFT)) + 
  scale_x_discrete(labels = c("ARS", "AW/DW", "BUR", "HOM", "MOT", "ROB", "SA", "TF/A", "T/O")) +
  xlab("OFFENSE") +
  scale_fill_discrete(name = "SHIFT")

ggplot() + 
  geom_bar(aes(x = crime$OFFENSE, fill = crime$crimeseason)) + 
  scale_x_discrete(labels = c("ARS", "AW/DW", "BUR", "HOM", "MOT", "ROB", "SA", "TF/A", "T/O")) +
  xlab("Offense") +
  scale_fill_discrete(name = "Season")

#ggplot() +
#  geom_bar(aes(x = crime1$METHOD, fill=crime1$OFFENSE)) +
#  scale_fill_discrete(name = "OFFENSE")+
#  xlab("Method")
```

This bar plot shows the freqency of different offenses in 4 seasons. Matching with the former part, the offense THEFT F/AUTO and THEFT/OTHER have the most two frequency. And almost all of offenses occur in the four seasons. 

To see if the offense the same across different crime time including seasons in one year and time in one day?
1.offense~seasons
H0: Offense and crime time for seasons in one year are independent.
H1:They are not independent.
We do the chi-squared to test this hypothesis and calculate the p-value. The outputs below are the summary of Chi-squared test and p-value.
```{r}
contable2=table(crime$OFFENSE,crime$crimeseason)
chisq.test(contable2)
```
Since the p-value is small, we conclude that offense and crime time for seasons in one year are not independent.

2.offense~time in one day
H0:Offense and crime time in one day are independent.
H1:They are not independent.
The same as the offense ~ seasons, we use the chi-squared to test the hypothesis and calculate the p-value.The outputs below are the summary of Chi-squared test and p-value.

```{r}
contable1=table(crime$OFFENSE,crime$SHIFT)
chisq.test(contable1)
```
The p-value here is still small, we conclude that offense and crime time in one day are not independent.
## Chapter 4: Report Time

From the dataset, we also found that there exists different time gap between the date of report and crime. We found it interesting for the reason that there may exists some relationship between the time difference with other variables including offense, location and crime time in one day.Therefore, In this part, we will explore more on this.

### 4.1 SMART Question

Does the time difference between report date and crime date have a correlation with offense, location and crime time in one day?

### 4.2 Data processing of time difference

First, as for the raw dataset only have columns report date and crime date, we need to acquire the time difference and created a new column named ‘time difference’ calculated by using column ‘report_date’ subtracting column ‘start_date’.The outputs are the summary of the time_difference.

```{r, echo=F}
crimeTime <- subset(crime, select = c(REPORT_DAT, START_DATE))
# levels(crimeTime$REPORT_DAT)
# crimeTime
# strptime(crime$REPORT_DAT[1],format = "%Y-%m-%d %H:%M:%S")
crimeTime$REPORT_DAT <- as.POSIXct(gsub(".000Z", "", gsub("T", " ", as.character(crimeTime$REPORT_DAT))))
#crimeTime$REPORT_DAT <- gsub("T"," ", crimeTime$REPORT_DAT)
#crimeTime$REPORT_DAT <- gsub(".000Z","", crimeTime$REPORT_DAT)
#crimeTime$REPORT_DAT <- as.POSIXct(crimeTime$REPORT_DAT)
crimeTime$START_DATE <- as.POSIXct(gsub(".000Z", "", gsub("T", " ", as.character(crimeTime$START_DATE))))
crimeTime <- crimeTime %>% 
  mutate(Time_Difference = difftime(REPORT_DAT, START_DATE))
crimeTime$Time_Difference <- as.numeric(crimeTime$Time_Difference)
head(crimeTime)
```
### 4.3.1 Is time difference affected by offense?

As there are some ineffective data in the column time_difference, which the vaule is less than 0, we only select the vaule difference between 0 and 1000.
```{r, echo = F}
crimeOffense <- subset(crime, select = 'OFFENSE')
crimeTimeAndOffense<- cbind(crimeTime, crimeOffense)

crimeTimeAndOffense <- subset(crimeTimeAndOffense, (Time_Difference <= 10000 & Time_Difference >= 0))
head(crimeTimeAndOffense)
```
```{r, echo = F}

p <- ggplot(crimeTimeAndOffense, aes(x=OFFENSE, y=Time_Difference, color = OFFENSE)) + 
  ggtitle("boxplot of Time with Offense") + 
  geom_boxplot()

p + scale_x_discrete(breaks = levels(crimeTimeAndOffense$OFFENSE), labels = c('ARS','AW/DW','BUR','HOM','MOT','ROB','SA','TF/A','T/O'))
```
Above are the graph of the time difference statistics grouped by offense in the box-plot, we can find that they are different obviously. The SEX ABUSE offense has the largest time difference. It mightly beccause  for some specific offense such as SEX ABUSE, people may not struggle inside and hesitate to report it due to self-esteem. However, for the homicide offense, people are more willing to report them in a hurry, so the time difference in it is relatively low. Besides, we found the range of ARSON offense is extremely small, wheras others are relatively large. 

To find if there are relationship between time difference an offense. We use statiscal inference further.
H0: The mean value of the time difference is the same across offense.
H1: They are different.
We use ANOVA to test the hypothesis and calculate the p-value.The outputs below are the summary of anova test and p-value.
```{r, echo =F }
anovaCrimeTaO <- aov(Time_Difference~OFFENSE, data = crimeTimeAndOffense)
anovaCrimeTaO
summary(anovaCrimeTaO)
```
Since the p-value is small, we reject the hypothesis that the mean value of the time difference is the same across offense.The report time after being attacked have relationsip with the crime offense. Victims seem to reluctant to report some specific offense such as SEX ABUSE as soon as possible.

#### 4.3.2 Is time difference affected by crime time in one day?
Similar with above, firstly we take a look at the time_difference distribution in the different shift of one day.The results are as follows. The range and average of time_difference in midnight is larger than another two. However, in the day, people are tend to report crime as soon as possbile, in which the average of difference is the smallest. 
```{r, echo = F}
crimeShift <- subset(crime, select = 'SHIFT')
crimeTimeAndShift<- cbind(crimeTime, crimeShift)
crimeTimeAndShift <- subset(crimeTimeAndShift, (Time_Difference <= 10000 & Time_Difference >= 0))

ggplot(crimeTimeAndShift, aes(x=SHIFT, y=Time_Difference, color = SHIFT)) + 
  ggtitle("boxplot of Time with Shift") + 
  geom_boxplot()
```
To find if there are some relationship between time difference and shift, we continue to do hypothesis test.

H0: The mean value of the time difference is the same across different time in one day.
H1: They are different.
We use ANOVA to test the hypothesis and calculate the p-value.The outputs are the summary of anova test, p-value and TukeyHSD.
```{r, echo =F }
anovaCrimeTaS <- aov(Time_Difference~SHIFT, data = crimeTimeAndShift)
anovaCrimeTaS
summary(anovaCrimeTaS)
```

```{r tukeyHSD}
tukeyAoV <- TukeyHSD(anovaCrimeTaS)
tukeyAoV 
```

We find the p-value is very small. We reject the null hypothesis that the mean value of the time difference is the same across different time in one day. Since the trend here is not clear, we want to know which pairs are different using TukeyHSD. The p-value for evening-day pair and midnight-day pair are extremely small, so we think they are significant. However, for the midnight-evening, the p-value is 0.67 which is larger than 0.05, we fail to reject the null hypothesis and think that the mean vaule of time differences are the same between this.